### 2021-01-12 LaTeX-USENIX/sections/paper.tex
define erc20
edits up to section 4

Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets. They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet. Order-driven trading can happen fully `on-chain' and this was experimented with in the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers. More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain. In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.

@@

\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain. An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work. The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).

@@

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an orderbook however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain orderbook is. We later compare it to our variant with rollups in Section~\ref{sec:rollups}. The main overlap is our common focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implement a priority queue with a heap that stores its data in a dynamically-sized array.

\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the priority queue smart contract.

@@

\paragraph{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache. We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty. The total gas cost for fully dequeuing the priority queue variants is outlined in Table~\ref{tab:PQUnitTests}. These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage. Recall this results in a gas refund. Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction). In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.

@@

Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market. Traders preload their account with ERC-20 tokens and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.

>>>>

Financial regulators seek to provide consumer protection during the issuing and trading of financial products and assets. They are concerned by their limited ability to intervene when trading is conducted on decentralized networks that, like Ethereum, run on the open internet. Order-driven trading can happen fully `on-chain' and this was experimented within the early days of Ethereum, but it has been largely abandoned for performance reasons in favour of running on centralized servers. More specifically, the core functionality is performed off-chain (\eg matching orders) while other aspects (\eg loading accounts, order cancellation) might be performed on-chain. In this world, company names, employees, addresses, and publicly addressable servers all provide regulatory hooks.

@@

\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain. An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work. The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, and fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).

@@

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

The most similar academic work to this paper is the TEX exchange~\cite{khalil2019tex}. TEX is also an implementation of an order book, however it uses on-chain and off-chain components, and does not answer our research question of how feasible an on-chain order book is. We later compare it to our variant with rollups in Section~\ref{sec:rollups}. The main overlap is our common focus on resisting front-running attacks. In a recent survey on front-running attacks in blockchain~\cite{eskandari2019sok}, three solutions are proposed. One solution is to provide confidentiality over the content of orders which is the approach taken by TEX. The main downside is that honest traders cannot submit their orders and leave, they must interact in a second round to reveal their orders. The second solution is to sequence transactions according to some rule, either at the protocol level~\cite{MZGA20} or as a third party service~\cite{Kla20} (a regulatory hook). These are very recent works and are not available for experimentation on Ethereum yet (although Chainlink has announced an intention\footnote{A. Juels. \href{https://blog.chain.link/chainlink-fair-sequencing-services-enabling-a-provably-fair-defi-ecosystem/}{blog.chain.link}, 11 Sep 2020.}). The third solution is to design the service in a way that front-running attacks are not profitable---this is the approach we take here.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implement a PQ with a heap that stores its data in a dynamically-sized array.

\item \textbf{Heap with Static Array.} A heap can be also represented by a Solidity storage array in which the storage is statically allocated. To do this, we pass the required size of the array as a constructor parameter to the PQ smart contract.

@@

\paragraph{Enqueue Performance.} We implemented, deployed, and tested each PQ using Truffle and Ganache. We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\paragraph{Dequeue Performance.} For each PQ variant storing 50 random integers, the \texttt{Dequeue()} function is iterated until the data structure is empty. The total gas cost for fully dequeuing the PQ variants is outlined in Table~\ref{tab:PQUnitTests}. These tests are performed using the following Ethereum gas metrics: block gas limit $=$11,741,495 and 1 gas $=$ 56 Gwei.\footnote{EthStats (July 2020): \url{https://ethstats.net/}} Dequeuing removes data from the contract's storage. Recall this results in a gas refund. Based on our manual estimates (EVM does not expose the refund counter), every variant receives the maximum gas refund possible (\ie half the total cost of the transaction). In other words, each of them actually consumes twice the \texttt{gasUsed} amount in gas before the refund, however none of them are better or worse based on how much of a refund they generate.

@@

Beyond the cleaning up issues with priority queues in Section~\ref{sec:gasrefund}, \cm also uses mappings with each market. Traders preload their account with tokens to be traded (which comply with a common token standard called ERC20) and/or ETH. \cm tracks what they are owed using a mapping called \texttt{totalBalance} and allows traders to withdraw their tokens at any time. However if a trader submits an order (\ie ask for their tokens), the tokens are committed and not available for withdrawal until the market closes (after which, the tokens are either transferred to the buyer or, if the trade is not executed, returned to the trader). Committed tokens are also tracked in a mapping called \texttt{unavailableBalance}. Sellers can request a token withdrawal up to their total balance subtracted by their unavailable balance.
